\documentclass{article}

\usepackage[numbers]{natbib} 

\begin{document}
	
	\title{Document that Consists of Two Paragraphs with a minimum of 10 Citations in it and Displaying the References in the Section}
	\date{}
	
	\maketitle
	
	
	\paragraph{Paragraph 1}
	
	The theory of relativity has been explored extensively in various scientific papers \citep{author1, author2, author3}. Einstein's contributions to physics are profound and have paved the way for many modern discoveries \citep{author4, author5}. Researchers continue to
	investigate the complexities of spacetime and the universe \citep{author6, author7}. These advancements have led to new methods of measurement and analysis in cosmology \citep{author8}.
	
	
	\paragraph{Paragraph 2}
	
	Recent studies have focused on the impact of climate change on various ecosystems \citep{author9, author10}. Scientists are examining how rising temperatures and changing weather patterns affect biodiversity and human health \citep{author11, author12}. Furthermore, interdisciplinary research has brought about innovative solutions for sustainable development \citep{author13}. Collaboration among experts from different fields is essential to address the challenges of global warming \citep{author14}.
	
	
	
	\newpage 
	
	\begin{thebibliography}{99}
		
		\bibitem{author1} Author One. \textit{Title of Article One}. Journal Name, vol. 10, no. 1, pp. 1--10, 2022.
		\bibitem{author2} Author Two. \textit{Title of Book Two}. Publisher Name, 2021.
		
		\bibitem{author3} Author Three. \textit{Title of Conference Paper Three}. In: Proceedings of Conference, pp. 100--110, 2020.
		
		
		\bibitem{author4} Author Four. \textit{Title of Article Four}. Journal Name, vol. 9, no. 2, pp. 15--25, 2019.
		\bibitem{author5} Author Five. \textit{Title of Book Five}. Publisher Name, 2018.
		
	\end{thebibliography}
	
	\end{document}
		
